---
title: "Hindcast Case Studies"
subtitle: "Tropical Tunas: Indian Ocean Yellowfin"
author: "Laurence Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  pdf_document:
       includes:
            in_header: header.tex 
---
  
```{r knitr_init, echo=FALSE, results="hide"}
library(knitr)
## Global options
opts_chunk$set(echo    =FALSE,
               eval    =TRUE,
               cache   =TRUE,
               cache.path="../cache/xval/",
               prompt  =FALSE,
               comment =NA,
               message =FALSE,
               tidy    =FALSE,
               warning =FALSE,
               fig.height=6,
               fig.width =8,
               fig.path  ="../tex/final-",
               dev       =c("png"))

options(digits=3)

iFig=0
```
```{r, pkgs, echo=FALSE, message=FALSE}
library(plyr)
library(dplyr)
library(ggplot2)
library(reshape)
library(reshape2)

library(r4ss)
library(stringr)
library(plyr)
library(dplyr)
library(xvl)

library(diags)

library(GGally)

library(Metrics)

library(plotrix)

library(rdrop2)

library(xtable)
```

```{r}
dirDrop="/home/laurence-kell/Dropbox/xval/io-yft"
```

```{r, eval=FALSE}
SS_doRetro(masterdir=file.path(dirDrop,"base"), oldsubdir="",newsubdir="retros",years=0:64,exefile=NULL)
SS_doRetro(masterdir=file.path(dirDrop,"aspm"), oldsubdir="",newsubdir="retros",years=0:64,exefile=NULL)
```

```{r, funcs}
mase<-function(obs,hat){
   t=length(hat)
   sum(abs(obs-hat))/sum(abs(obs[-1]-obs[-length(obs)]))*(t-1)/t}

mh<-function (actual, predicted, step_size = 1)
{
naive_start <- step_size + 1
n <- as.numeric(length(actual))
naive_end <- n - step_size
sum_errors <- sum(ae(actual, predicted))
naive_errors <- sum(ae(actual[naive_start:n], actual[1:naive_end]))
return(sum_errors/(n * naive_errors/naive_end))
}

```

# Retrospective

```{r, retro-data}
getPath <- function(file) {
  if (!grepl(.Platform$file.sep,file))
    res <- getwd()
  else
    res <- substr(file,1,max(gregexpr(.Platform$file.sep,file)[[1]])-1)
  return(res)}

getFile<-function(file) {
  res <- substr(file,max(gregexpr(.Platform$file.sep,file)[[1]])+1,
                nchar(file))
  return(res)}


x    =substr(getFile(system2("ls",args=file.path(dirDrop,"base/hyrs/kobe*"),stdout=TRUE)),5,7)
base=mdply(x, function(tail) data.frame(tail=tail,read.table(paste(file.path(dirDrop,"base/hyrs/kobe"),tail,".csv",sep=""))))[,-1]
names(base)[2]="Yr"

x    =substr(getFile(system2("ls",args=file.path(dirDrop,"aspm/hyrs/kobe*"),stdout=TRUE)),5,7)
aspm=mdply(x, function(tail) data.frame(tail=tail,read.table(paste(file.path(dirDrop,"aspm/hyrs/kobe"),tail,".csv",sep=""))))[,-1]
names(aspm)[2]="Yr"

load(file.path(file.path(dirDrop,"jabba","jabba-ky.RData")))
names(ky)[c(2,6:7)]=c("Yr","stock","harvest")

retro=rbind(cbind(run="base",base),
            cbind(run="aspm",aspm),
            cbind(run="jabba",ky[,c("Yr","tail","stock","harvest")]))
retro$tail   =as.numeric(retro$tail)
retro$Yr     =as.numeric(retro$Yr)
retro$stock  =as.numeric(retro$stock)
retro$harvest=as.numeric(retro$harvest)

retro=mutate(retro,  year        =(Yr-1)%/%4+1947,
                     quarter     =Yr-(year-1950)*4-12,
                     tail.year   =(tail-1)%/%4+1947,
                     tail.quarter=tail-(tail.year-1950)*4-12)

dat=subset(retro,year<=2017&quarter==4&tail.quarter==4)[,c("run","tail.year","year","stock","harvest")]
dat=melt(dat,id=c("run","tail.year","year"))
dat=subset(dat,year>=2001)
#dat$run=factor(dat$run,levels=c("base","aspm","jabba"),
#                       labels=c("SS",  "ASPM","JABBA"))
```


```{r}
save(dat,file="/home/laurence-kell/Desktop/papers/xval-yftio/results/retro.RData")
```

```{r, retro}
dat$model=factor(dat$run,levels=c("base","aspm","jabba"),labels=c("Base","ASPM","JABBA"))
ggplot(subset(dat,year<=tail.year))+
  geom_line(aes(year,value),  data=subset(dat,tail.year==2016),col="black",lwd=1.5)+
  facet_grid(variable~model,scale="free")+
  theme_bw()+theme(legend.position="bottom")+
  geom_hline(aes(yintercept=1))+
  geom_line(aes(year,value,group=tail.year,col=year<tail.year))+
  geom_point(aes(year,value), data=subset(dat,tail.year==year),  col="brown")+
  #geom_line(aes(year,value),  data=subset(dat,tail.year==year),  col="brown",linetype=3)+
  #geom_point(aes(year,value), data=subset(dat,tail.year==year-3),  col="blue")+
  #geom_line(aes(year,value),  data=subset(dat,tail.year==year-3),  col="blue", linetype=3)+
  xlab("Year")+ylab("Relative to Benchmark")
```

**Figure `r iFig=iFig+1; iFig`** Retrospective analyses.

```{r, retro3}
dat$model=factor(dat$run,levels=c("base","aspm","jabba"),labels=c("Base","ASPM","JABBA"))
ggplot(subset(dat,year<=tail.year+3))+
  geom_line(aes(year,value),  data=subset(dat,tail.year==2016),col="black",lwd=1.5)+
  facet_grid(variable~model,scale="free")+theme_bw()+theme(legend.position="bottom")+
  geom_hline(aes(yintercept=1))+
  geom_line(aes(year,value,group=tail.year,col=year<tail.year))+
  geom_point(aes(year,value), data=subset(dat,tail.year==year-3),  col="blue")+
  #geom_line(aes(year,value),  data=subset(dat,tail.year==year-3),  col="blue", linetype=3)+
  xlab("Year")+ylab("Relative to Benchmark")
```

**Figure `r iFig=iFig+1; iFig`** Retrospective analyses (cyan) with 3 year projections (pink); the thick black line is the assessed estimates, the brown points the terminal years and blue points are the 3 step ahead projections.


```{r, retro-all,fig.height=8}
dat$model=factor(dat$run,levels=c("base","aspm","jabba"),labels=c("Base","ASPM","JABBA"))
dat=rbind(cbind(Steps="Retrospective", subset(dat,year<=tail.year)),
          cbind(Steps="3-step",subset(dat,year<=tail.year+3)))

dat$Steps=factor(dat$Steps,levels=c("Retrospective","3-step"))

ggplot(dat)+
  geom_line(aes(year,value),  data=subset(dat,tail.year==2016),col="black",lwd=1.5)+
  facet_grid(Steps+variable~model,scale="free")+theme_bw()+theme(legend.position="bottom")+
  geom_hline(aes(yintercept=1))+
  geom_line(aes(year,value,group=tail.year,col=year<tail.year))+
  geom_point(aes(year,value), data=subset(dat,tail.year==year),    fill="cyan",col="black",shape=23)+
  geom_point(aes(year,value), data=subset(dat,tail.year==year-1),  col="brown")+
  geom_point(aes(year,value), data=subset(dat,tail.year==year-3),  col="blue")+
  #geom_line(aes(year,value),  data=subset(dat,tail.year==year-3),  col="blue", linetype=3)+
  xlab("Year")+ylab("Relative to Benchmark")
```

**Figure `r iFig=iFig+1; iFig`** Retrospective analyses (cyan) with 3 (blue), 1 (brown)  projections the thick black line is the assessed estimates, the brown points the terminal years and blue points are the projections.



# CPUE

```{r, cpue-data}
base=SS_output(file.path(dirDrop,"base"),ncols=320,forecast=FALSE, verbose=FALSE, printstats=FALSE)
aspm=SS_output(file.path(dirDrop,"aspm"),ncols=320,forecast=FALSE, verbose=FALSE, printstats=FALSE)

load(file.path(dirDrop,"jabba/yftio/yftio_Base_jabba.rdata"))

u=rbind(cbind(run="base",base$cpue),
        cbind(run="aspm",aspm$cpue))

u=rbind(transmute(u,run=run,name=Fleet_name,yr=Yr,obs=Obs),
        transmute(melt(jabba$inputseries$cpue,id="Yr"),yr=Yr,run="jabba",name=substr(variable,1,7),obs=value))

#The fist quarter of the fist year 1950 has the time 13
u=mutate(u, year   =(yr-1)%/%4+1947,
            quarter=yr-(year-1950)*4-12)
```

```{r}
save(u,file="/home/laurence-kell/Desktop/tmp/u.RData")
```

```{r, residuals-data, fig.height=10}
load(file.path(dirDrop,"jabba/yftio/yftio_Base_jabba.rdata"))
source('~/Desktop/flr/diags/R/diags-SS.R')
source('~/Desktop/flr/diags/R/diags-funcs.R')

dgs=rbind(cbind(run="base",.diagUss(file.path(dirDrop,"base"))),
          cbind(run="aspm",.diagUss(file.path(dirDrop,"aspm"))))[,c("run","name","year","season","obs","hat","residual")]
dgs=rbind(dgs,cbind(run="jabba",jabba$diags[,c("name","year","season","obs","hat","residual")]))

dgs=mutate(dgs, yr     =(year-1)%/%4+1947,
                quarter=year-(yr-1950)*4-12,
                name  =substr(name,1,7))
```

```{r}
save(dgs,file="/home/laurence-kell/Desktop/tmp/t.RData")
```


```{r, cpue-residual-runs, fig.height=10,fig.width=8}
library(qicharts2)

dgs$name=factor(dgs$name,labels=c("CPUE 1","CPUE 2","CPUE 3","CPUE 4"))

dgs$residual=log(dgs$obs/dgs$hat)
runs=ddply(dgs, .(run,name,quarter), with, qic(year,residual,chart="i")$data)
runs=ddply(runs,.(run,name,quarter),with, 
               data.frame(crossings=all(n.crossings>n.crossings.min),
                          runs     =all(longest.run<longest.run.max)))
runs=transform(runs,Pass=runs&crossings)

runs$model=factor(runs$run,levels=c("base","aspm","jabba"),labels=c("Base","ASPM","JABBA"))
dgs$model=factor(dgs$run,levels=c("base","aspm","jabba"),labels=c("Base","ASPM","JABBA"))
ggplot(dgs)+ 
  geom_hline(aes(yintercept=0))+
  geom_line(aes(year,residual),position=position_dodge(width=1),col="grey60")+
  geom_point(aes(year,residual),position=position_dodge(width=1),col="red",lwd=0.5,
             data=subset(dgs,residual<0))+
  geom_linerange(aes(year,ymin=0,ymax=residual),position=position_dodge(width=1),col="red",lwd=0.5,
             data=subset(dgs,residual<0))+
  geom_point(aes(year,residual),position=position_dodge(width=1),col="black",lwd=0.5,
             data=subset(dgs,residual>0))+
  geom_linerange(aes(year,ymin=0,ymax=residual),position=position_dodge(width=1),col="black",lwd=0.5,
             data=subset(dgs,residual>0))+
  theme(legend.position="bottom")+
  facet_grid(name+quarter~model,scale="free",space="free_x")+
  theme_bw(14)+
  theme(legend.position="bottom",strip.text.y=element_text(angle=0),
                                 strip.text.x=element_text(angle=0),
                                 axis.text.x=element_text(angle=45, hjust=1))+ 
  xlab("Year")+ylab("")+
  geom_rect(aes(fill=Pass), xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf, alpha=0.25,
            data=runs)+
     scale_fill_manual(values=c("red","green"))+
     scale_x_continuous(breaks=seq(1950,2010,10))
```

```{r, base-retro}
load(file.path(dirDrop,"base/hy.RData"))
dat =subset(merge(hy[[2]],hy[[5]][,c(1:2,4)]),year>220)
names(dat)[4]="Yr"

basey=mutate(dat, year  =(Yr-1)%/%4+1947,
                  quarter=Yr-(year-1950)*4-12)
```


```{r, aspm-retro}
load(file.path(dirDrop,"aspm/hy.RData"))
dat =subset(merge(hy[[2]],hy[[5]][,c(1:2,4)]),year>220)
names(dat)[4]="Yr"

aspmy=mutate(dat, year   =(Yr-1)%/%4+1947,
                 quarter=Yr-(year-1950)*4-12)
```


```{r, jabba-retro}
load(file.path(dirDrop,"jabba/jabba-hy.RData"))
names(hy)[5]="Yr"

jabby=mutate(hy, year   =(Yr-1)%/%4+1947,
                 quarter=Yr-(year-1950)*4-12,
                 name  =substr(name,1,7))

```


```{r, hy-data}
hy=rbind(cbind(run="base",basey), 
         cbind(run="aspm",aspmy)) 

hy=rbind(transmute(hy,   run=run,     name=name,year=year,quarter=quarter,tail=tail,yr=Yr,obs=obs,hat=hat),
         transmute(jabby,run="flabba",name=name,year=year,quarter=quarter,tail=tail,yr=Yr,obs=obs,hat=hat))

hy=mutate(hy,  tail.year   =(tail-1)%/%4+1947,
               tail.quarter=tail-(tail.year-1950)*4-12)  
```

\newpage


```{r, stats}
stats=ddply(subset(hy,tail==yr),.(run,name,quarter),   
            with, {
              obs=obs[order(year)]
              hat=hat[order(year)]
              data.frame(rmse=rmse(log(obs),log(hat)), 
                             mae =mae( log(obs),log(hat)),
                             mase=Metrics:::mase(log(obs),log(hat)),
                             mape=mape(log(obs),log(hat)),
                             rse = rse(log(obs),log(hat)),
                             sd  = var(log(obs/hat))^0.5,
                             cor = cor(log(obs),log(hat)))})  

stats$model=factor(stats$run,levels=c("base","aspm","flabba"),labels=c("Base","ASPM","JABBA")) 
save(stats,file="/home/laurence-kell/Desktop/papers/xval-yftio/results/stats.RData")
```

```{r, hy-plot, fig.height=10}
hy$name=factor(hy$name,labels=c("CPUE 1","CPUE 2","CPUE 3","CPUE 4"))
stats$name =factor(stats$name, labels=c("CPUE 1","CPUE 2","CPUE 3","CPUE 4"))

hy$model=factor(hy$run,levels=c("base","aspm","flabba"),labels=c("Base","ASPM","JABBA"))
ggplot(subset(hy,yr>220&yr<=tail&tail.quarter==quarter))+
  geom_line(aes(year,hat,group=paste(tail,model)),col="grey50")+  
  geom_point(aes(year,obs),data=subset(hy,tail==yr),col="red")+  
  geom_point(aes(year,hat),data=subset(hy,tail==yr))+
  facet_grid(name+quarter~model,scale="free")+
  theme_bw()+ theme(legend.position="bottom")+
  theme(legend.position="bottom",strip.text.y=element_text(angle=0),
                                 strip.text.x=element_text(angle=0),
                                 axis.text.x=element_text(angle=45, hjust=1))+ 
  scale_color_manual(values=c("blue","brown","darkblue"))+
  geom_rect(aes(fill=Pass), xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf, alpha=0.25,
            data=transform(stats,Pass=mase<1))+
  scale_fill_manual(values=c("red","green"))+
  scale_x_continuous(breaks=seq(1970,2020,10))
```

**Figure `r iFig=iFig+1; iFig`** Time series of CPUE indices for hindcast by **quarter, year and series**, observations (red) and estimates from hindcast (blue).


```{r, stats3}
stat3=ddply(subset(hy,tail+3==yr),.(run,name,quarter),   
            with, {
              obs=obs[order(year)]
              hat=hat[order(year)]
              data.frame(rmse=rmse(log(obs),log(hat)), 
                             mae =mae( log(obs),log(hat)),
                             mase=Metrics:::mase(log(obs),log(hat)),
                             mape=mape(log(obs),log(hat)),
                             rse = rse(log(obs),log(hat)),
                             sd  = var(log(obs/hat))^0.5,   
                             cor = cor(log(obs),log(hat)))})

stat3$model=factor(stat3$run,levels=c("base","aspm","flabba"),labels=c("Base","ASPM","JABBA"))
save(stat3,file="/home/laurence-kell/Desktop/papers/xval-yftio/results/stat3.RData")
```


```{r, hy3-plot, fig.height=10}
hy$name=factor(hy$name,labels=c("CPUE 1","CPUE 2","CPUE 3","CPUE 4"))
stat3$name =factor(stat3$name, labels=c("CPUE 1","CPUE 2","CPUE 3","CPUE 4"))
hy$model=factor(hy$run,levels=c("base","aspm","flabba"),labels=c("Base","ASPM","JABBA"))
ggplot(subset(hy,yr>220&year<=tail.year+3&tail.quarter==quarter))+        
  geom_line(aes(year,hat,group=paste(tail,run)),col="grey50",lwd=0.25)+
  geom_point(aes(year,obs),data=subset(hy,tail==yr),col="red")+
  geom_point(aes(year,hat),data=subset(hy,tail.year==year-3&tail.quarter==quarter),col="black")+
  #geom_point(aes(year,hat),data=subset(hy,tail.year==year-1&tail.quarter==quarter),col="blue")+
  facet_grid(name+quarter~model,scale="free")+
  theme_bw()+ theme(legend.position="bottom")+
  theme(legend.position="bottom",strip.text.y=element_text(angle=0),
                                 strip.text.x=element_text(angle=0),
                                 axis.text.x=element_text(angle=45, hjust=1))+ 
  geom_rect(aes(fill=Pass), xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf, alpha=0.25,
            data=transform(stat3,Pass=mase<1))+
  scale_fill_manual(values=c("red","green"))+
  scale_x_continuous(breaks=seq(1970,2020,10))
```

**Figure `r iFig=iFig+1; iFig`** Time series of CPUE indices with 3 steps ahead for hindcast by **quarter, year and series**, observations (red) and estimates from hindcast (blue).

```{r}
save(hy,file="/home/laurence-kell/Desktop/tmp/hy.RData")
```

\blandscape

```{r, hy-plot-all, fig.width=12, fig.height=8}
hy$name=factor(hy$name,labels=c("CPUE 1","CPUE 2","CPUE 3","CPUE 4"))
hy=rbind(cbind(Steps="1-step", subset(hy,yr>220&year<=tail.year  &tail.quarter==quarter)),
         cbind(Steps="3-steps",subset(hy,yr>220&year<=tail.year+3&tail.quarter==quarter)))
stat=rbind(cbind(Steps="1-step", stats),
           cbind(Steps="3-steps",stat3))
stat=transform(stat,Pass=mase<1)
stat$name =factor(stats$name, labels=c("CPUE 1","CPUE 2","CPUE 3","CPUE 4"))

ggplot(hy)+
  geom_line( aes(year,hat,group=paste(tail,model)),col="grey50")+  
  geom_point(aes(year,obs),data=subset(hy,tail==yr),col="red")+  
  geom_point(aes(year,hat),data=subset(hy,tail==yr))+
  facet_grid(name+quarter~Steps+model,scale="free")+
  theme_bw()+ theme(legend.position="bottom")+
  theme(legend.position="bottom",strip.text.y=element_text(angle=0),
                                 strip.text.x=element_text(angle=0),
                                 axis.text.x=element_text(angle=45, hjust=1))+ 
  scale_color_manual(values=c("blue","brown","darkblue"))+
  geom_rect(aes(fill=Pass), xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf, alpha=0.25,
            data=stat)+
  scale_fill_manual(values=c("red","green"))+
  scale_x_continuous(breaks=seq(1970,2020,10))
```

**Figure `r iFig=iFig+1; iFig`** Time series of CPUE indices for hindcast by **quarter, year and series**, observations (red) and estimates from hindcast (blue).

\elandscape
```{r,rsdl, fig.height=8,fig.width=4}
load("/home/laurence-kell/Desktop/tmp/hy.RData")
dat=subset(transform(hy,step=tail.year-year),quarter==tail.quarter&step<=0&step>=-5&year>=2000)
dat$Step=factor(dat$step,levels=-(0:5), labels=c("Model","1","2","3","4","5"))
dat$run =factor(dat$run,labels=c("SS","ASPM","JABBA"),levels=c("base","aspm","flabba"))
ggplot(dat)+
  geom_boxplot(aes(Step,obs/hat))+
  facet_grid(run~.)+
  theme_bw()+
  xlab("Step-A-Head")+ylab("Residual")+
  scale_y_log10()

```

\blandscape
```{r, taylor-hy-1, fig.width=12, fig.height=6}
par(mfrow=c(1,2))

dat=subset(hy,tail.year==year&tail.quarter==quarter)

with(subset(dat,model=="JABBA"&name=="CPUE 1"&quarter==1),
taylor.diagram(obs,
               hat,
               add=FALSE,col="red",pch=4,pos.cor=TRUE,
               #xlab="X Axis",
               #ylab="Y Axis",
               main="Taylor Diagram",
               show.gamma=TRUE,ngamma=3,sd.arcs=1,ref.sd=TRUE,
               grad.corr.lines=c(0.2,0.4,0.6,0.8,0.9),
               pcex=1,cex.axis=1,
               normalize=TRUE,
               mar=c(5,4,6,6),
               lwd=10,font=5,lty=3))

d_ply(dat,.(quarter,name,model), with, taylor.diagram(obs,hat,add=TRUE,normalize=TRUE,
                                                    col=c("Base"="red","Jabba"="blue","ASPM"="brown")[model[1]],
                                                    pch=c("CPUE 1"=1,"CPUE 2"=2,"CPUE 3"=3,"CPUE 4"=4)[name[1]]))

legend(1.5,1.5,cex=1.2,pt.cex=1.2,legend=c("BASE","ASPM", "JABBA","CPUE 1","CPUE 2","CPUE 3","CPUE 4"),
                                  col   =c("red", "blue","brown", "black",   "black",   "black",   "black"),
                                  pch   =c(1,1,1,1,2,3,4))

#hy=mutate(hy,  tail.year   =(tail-1)%/%4+1947,
#               tail.quarter=tail-(tail.year-1950)*4-12)

dat=subset(hy,tail.year==year-2&tail.quarter==quarter)

with(subset(dat,model=="JABBA"&name=="CPUE 1"&quarter==1),
taylor.diagram(obs,
               hat,
               add=FALSE,col="red",pch=4,pos.cor=TRUE,
               #xlab="X Axis",
               #ylab="Y Axis",
               main="Taylor Diagram",
               show.gamma=TRUE,ngamma=3,sd.arcs=1,ref.sd=TRUE,
               grad.corr.lines=c(0.2,0.4,0.6,0.8,0.9),
               pcex=1,cex.axis=1,
               normalize=TRUE,
               mar=c(5,4,6,6),
               lwd=10,font=5,lty=3))

d_ply(dat,.(quarter,name,model), with, taylor.diagram(obs,hat,add=TRUE,normalize=TRUE,
                                                    col=c("Base"="red","Jabba"="blue","ASPM"="brown")[model[1]],
                                                    pch=c("CPUE 1"=1,"CPUE 2"=2,"CPUE 3"=3,"CPUE 4"=4)[name[1]]))

legend(1.5,1.5,cex=1.2,pt.cex=1.2,legend=c("BASE","ASPM", "JABBA","CPUE 1","CPUE 2","CPUE 3","CPUE 4"),
                                  col   =c("red", "blue","brown", "black",   "black",   "black",   "black"),
                                  pch   =c(1,1,1,1,2,3,4))
```

**Figure `r iFig=iFig+1; iFig`** One and three step ahead fits.

\elandscape

```{r, cpue-prediction-runs, fig.height=10,fig.width=8}
library(qicharts2)

dat$residual=log(dat$obs/dat$hat)
runs=ddply(dat, .(run,name,quarter), with, qic(year,residual,chart="i")$data)
runs=ddply(runs,.(run,name,quarter),with, 
               data.frame(crossings=all(n.crossings>n.crossings.min),
                          runs     =all(longest.run<longest.run.max)))
runs=transform(runs,Pass=runs&crossings)

dat$model =factor(dat$run, levels=c("SS","ASPM","JABBA"),labels=c("Base","ASPM","JABBA"))
runs$model=factor(runs$run,levels=c("SS","ASPM","JABBA"),labels=c("Base","ASPM","JABBA"))

ggplot(dat)+ 
  geom_hline(aes(yintercept=0))+
  geom_line(aes(year,residual),position=position_dodge(width=1),col="grey60")+
  geom_point(aes(year,residual),position=position_dodge(width=1),col="red",lwd=0.5,
             data=subset(dat,residual<0))+
  geom_linerange(aes(year,ymin=0,ymax=residual),position=position_dodge(width=1),col="red",lwd=0.5,
             data=subset(dat,residual<0))+
  geom_point(aes(year,residual),position=position_dodge(width=1),col="black",lwd=0.5,
             data=subset(dat,residual>0))+
  geom_linerange(aes(year,ymin=0,ymax=residual),position=position_dodge(width=1),col="black",lwd=0.5,
             data=subset(dat,residual>0))+
  theme(legend.position="bottom")+  
  facet_grid(name+quarter~model,scale="free",space="free_x")+
  theme_bw(14)+
  theme(legend.position="bottom",strip.text.y=element_text(angle=0),
                                 strip.text.x=element_text(angle=0),
                                 axis.text.x=element_text(angle=45, hjust=1))+ 
  xlab("Year")+ylab("")
  #geom_rect(aes(fill=Pass), xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf, alpha=0.25,
  #          data=runs)+
  #   scale_fill_manual(values=c("red","green"))+
  #   scale_x_continuous(breaks=seq(1950,2010,10))
```

**Figure `r iFig=iFig+1; iFig`** Residuals for scenarios by year, red background indicates unusually long runs or unusually few crossings.

```{r, cpue-plot}
ggplot(u)+
  geom_path(aes(year,obs,col=run))+
  facet_grid(name~quarter,scale="free")+
  theme(legend.position="bottom")+
  xlab("Year")+ylab("CPUE")
```

**Figure `r iFig=iFig+1; iFig`** CPUEs as used by the three models.

```{r, residual-plot, fig.height=10}
ggplot(dgs)+
  geom_hline(aes(yintercept=0))+
  #geom_line(aes(yr,residual, col=run),linetype=3)+
  geom_point(aes(yr,residual,col=run),position=position_dodge(width = 2),size=0.2)+
  geom_smooth(aes(yr,residual,col=run),se=FALSE)+
  #geom_linerange(aes(yr,ymin=0,ymax=residual,col=run),position=position_dodge(width = 2))+
  facet_grid(name~quarter)+
  theme_bw()+
  theme(legend.position="bottom")+
  xlab("Year")+ylab("Residuals")
```

**Figure `r iFig=iFig+1; iFig`** Residuals.

\newpage
## RMSE


```{r, pairs}
ggpairs(stats[,-(1:3)])
```

**Figure `r iFig=iFig+1; iFig`** Metrics.


```{r cpue-correlations, fig.height=8,fig.width=8}
library(GGally)

load("/home/laurence-kell/Desktop/tmp/u.RData")
u=cast(subset(u,run=="base"),year+quarter~name,value="obs")

my_density <- function(data,mapping,...){
  ggplot(data=data,mapping=mapping)+
    geom_density(...,lwd=1)}

my_smooth <- function(data,mapping,...){
  ggplot(data=data,mapping=mapping)+
    geom_smooth(...,method="lm",se=FALSE)+
    geom_point(...)}

ggpairs(u[,-1],
        mapping=aes(color=as.factor(quarter)),
        #legend = 1,
        columns = 2:5, 
  upper=list(continuous=wrap("cor",size=4, hjust=0.5)),
  lower=list(continuous = wrap(my_smooth)),
  diag=list(continuous="bar"),
    title = "")+theme_bw(14)+
  theme(legend.position ="none", 
       panel.grid.major =element_blank(), 
       axis.ticks       =element_blank(), 
       axis.text.x      =element_blank(), 
       axis.text.y      =element_blank(),
       panel.border     =element_rect(linetype = 1, colour="black", fill=NA)) 
```
**Figure `r iFig=iFig+1; iFig`.** Pairwise scatter plots to look at correlations between Indices.


```{r cpue-ccf, fig.height=8,fig.width=8}
library(FLCore)

my_ccf<-function(cpue){
  cc=mdply(expand.grid(a=names(cpue),b=names(cpue)),
           function(a,b){
             #print(paste(a,b))
             res=model.frame(mcf(FLQuants(cpue[c(a,b)])))
             res=subset(res,!is.na(res[,7])&!is.na(res[,8]))
             
             if (dim(res)[1]>10){
               res=data.frame(lag=-7:7,data=ccf(res[,7],res[,8],plot=F,
                                                lag.max=7)$acf)
               return(res)}else{return(NULL)}}
  )}

load("/home/laurence-kell/Desktop/tmp/u.RData")
u=subset(u,run=="base")

cc=my_ccf(FLQuants(dlply(u,.(name,quarter),with,
                         as.FLQuant(data.frame(year=year,data=obs)))))

ggplot(cc)+
  geom_linerange(aes(x=lag,ymin=0,ymax=data))+
  facet_grid(a~b)+
  geom_vline(aes(xintercept=0))+
  theme_bw(14)+
  theme(legend.position="bottom",strip.text.x=element_text(angle=90),
                                 strip.text.y=element_text(angle=0))
```
**Figure `r iFig=iFig+1; iFig`** Cross correlations between indices, to identify potential lags due to year-class effects.

```{r cpue-clusters, fig.height=8,fig.width=8}
library(corrplot)

load("/home/laurence-kell/Desktop/tmp/u.RData")
u=cast(subset(u,run=="base"),year~name+quarter,value="obs")


cr=cor(u[,-1],use="pairwise.complete.obs")  
dimnames(cr)=list(names(u)[-1],names(u)[-1])
cr[is.na(cr)]=0
corrplot(cr,diag=F,order="hclust",addrect=4)  +          
             theme(legend.position="bottom")  
```
**Figure `r iFig=iFig+1; iFig`.** Plot of the correlation matrix for the CPUE indices, blue indicate a positive correlation  and red negative. the order of the indices and the rectanglur boxes are chosen based on a hierarchical cluster analysis using a set of dissimilarities for the indices being clustered.


## Model-based
```{r}
load("/home/laurence-kell/Desktop/papers/xval-yftio/results/retro.RData")

peel=subset(dat,tail.year==year)[,c("run","variable","tail.year","value")]
names(peel)[3]="year"
ref =subset(dat,tail.year==2016)[,c("run","variable","year","value")]
dat=merge(ref,peel,by=c("run","variable","year"))

ggplot(dat)+
  geom_point(aes(year,value.x))+
  geom_point(aes(year,value.y,col="red"))+
  facet_grid(variable~run)

tab=ddply(dat,.(variable,run), with, data.frame(rho=mean((value.y-value.x)/value.x),
                                                re =mean(log(value.y)/value.x)))

print(xtable(tab),file="/home/laurence-kell/Desktop/papers/xval-yftio/tex/tab1.tex")
```

```{r}
load("/home/laurence-kell/Desktop/papers/xval-yftio/results/retro.RData")

prj=subset(dat,tail.year+3==year)[,c("run","variable","tail.year","value")]
prj$year=prj$tail.year+3
ref=subset(dat,tail.year==2016)[,c("run","variable","year","value")]
dat=merge(ref,prj,by=c("run","variable","year"))

ggplot(dat)+
  geom_point(aes(year,value.x))+
  geom_point(aes(year,value.y,col="red"))+
  facet_grid(variable~run)

tab=ddply(dat,.(variable,run), with, data.frame(rho=mean((value.y-value.x)/value.x),
                                                re =mean(log(value.y)/value.x)))
tab
print(xtable(tab),file="/home/laurence-kell/Desktop/papers/xval-yftio/tex/tab2.tex")
```


## MASE
```{r, mase}
load("/home/laurence-kell/Desktop/papers/xval-yftio/results/stat3.RData")

my_density <- function(data,mapping,...){
  ggplot(data=data,mapping=mapping)+
    geom_density(...,lwd=1)}

my_smooth <- function(data,mapping,...){
  ggplot(data=data,mapping=mapping)+
    geom_smooth(...,method="lm",se=FALSE)+
    geom_point(...)}

ggpairs(stat3,
        columns=c("mase","rmse","sd","cor"),
  mapping = ggplot2::aes(color=run,shape=name),
  upper=list(continuous=wrap("cor",size=4, hjust=0.5)),
  lower = list(continuous = wrap(my_smooth,size=1,shape=21)),
  diag = list(continuous = wrap("densityDiag",alpha=.1)),
  #diag=list(continuous=wrap(my_density,alpha=0.2)),
  title = "")+theme_bw(14)+
  theme(legend.position ="none", 
       panel.grid.major =element_blank(), 
       axis.ticks       =element_blank(), 
       axis.text.x      =element_blank(), 
       axis.text.y      =element_blank(),
       panel.border     =element_rect(linetype = 1, colour="black", fill=NA)) 
```

```{r}
load("/home/laurence-kell/Desktop/papers/xval-yftio/results/stat3.RData")

tab=cast(melt(stat3[,c("model","name","quarter","mase","rmse","cor","sd")],id=c("model","name","quarter")),
         name+quarter~variable+model)
tab=xtable(tab)

print(tab,file="/home/laurence-kell/Desktop/papers/xval-yftio/tex/tab3.tex")

```


```{r}
load("/home/laurence-kell/Desktop/papers/xval-yftio/dan/CPUE_1_input.RData")

u=CPUE_1_INPUT_OBJECT[['data']];

ggplot(subset(mutate(u,Year=yq,CPUE=pr_7994_m8,Index=AssessmentAreaName),Year>1972))+
  geom_line(aes(Year,CPUE,col=Index))
```


```{r}
ctc=read.csv("/home/laurence-kell/Desktop/papers/xval-yftio/dan/YFT_SS3_scenario2_Rev2.csv")[,1:5]
ctc=ddply(transform(ctc,Gear=FisheryCode=="LL"),.(Year,AssessmentArea,Gear), with, data.frame(Catch=sum(Catch)))
  
ggplot(ctc)+
  geom_area(aes(Year,Catch,fill=as.character(Gear)))+
  facet_grid(AssessmentArea~.)

```

